### 2012-12-27 inst/examples/allee.Rmd
example without harvest in observation stage

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
#opts_chunk$set(dev = 'Cairo_pdf', dev.args=list(""))
opts_chunk$set(dev="png", dev.args=list(bg="transparent"))
opts_chunk$set(comment=NA, tidy=FALSE)
theme_set(theme_bw(base_size=16))
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

@@

```{r sdp-pars-explore}
sigma_g <- 0.05
sigma_m <- 0.02
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```

@@

  Xo <- K # observations start from
  x0 <- Xo # simulation under policy starts from
  obs <- sim_obs(Xo, z_g, f, p, Tobs=40, seed = seed_i)
  alt <- par_est(obs)
  est <- par_est_allee(obs, f, p)
  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=FALSE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f, est$p, alt$f, alt$p, x_grid, obs, seed_i)
#  posteriors_plot(gp, priors) # needs trace=TRUE!
  OPT <- optimal_policy(gp, f, est$f, alt$f,
                        p, est$p, alt$p,
                        x_grid, h_grid, sigma_g, 
                        est$sigma_g, alt$sigma_g, 
                        delta, xT, profit, reward, OptTime)
  plot_policies(x_grid, OPT$gp_D, OPT$est_D, OPT$true_D, OPT$alt_D)
  dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
  sim_plots(dt, seed=seed_i)
  profits_stats(dt)
```

```{r}
matrices_gp <- gp_transition_matrix(gp$ZZ.km, gp$ZZ.vark, x_grid, h_grid) # 
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, OptTime, xT, profit, delta, reward=reward)
```

```{r}
matrices_same <- gp_transition_matrix(sapply(x_grid, f, 0, p), gp$ZZ.vark, x_grid, h_grid) 
opt_same <- find_dp_optim(matrices_same, x_grid, h_grid, OptTime, xT, profit, delta=delta, reward = reward)
```

```{r}
matrices_true <- f_transition_matrix(f, p, x_grid, h_grid, sigma_g)
opt_true <- find_dp_optim(matrices_true, x_grid, h_grid, OptTime, xT, profit, delta=delta, reward = reward)
```

```{r}
dd <- melt(data.frame(x=x_grid, gp= opt_gp$D[,1], same=opt_same$D[,1], true=opt_true$D[,1]), id="x")
ggplot(dd) + geom_point(aes(x, value, col=variable))
```

>>>>

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
#opts_chunk$set(dev = 'Cairo_pdf', dev.args=list(""))
opts_chunk$set(dev="png", dev.args=list(bg="transparent"))
opts_chunk$set(comment=NA, tidy=FALSE)
theme_set(theme_bw(base_size=16))
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
#sha <- gsub("^commit ", "", system("git log -n 1", intern=TRUE)[1])
#short_sha <- gsub("(^.{10}).*", "\\1", sha)
#date <- format(Sys.time(), "%Y-%m-%d-%H-%M-%S")
#opts_chunk$set(fig.path = paste("figure/", date, "-", short_sha, "-", sep=""))

@@

```{r sdp-pars-explore}
sigma_g <- 0.05
sigma_m <- 0.0
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```

@@

  Xo <- K # observations start from
  x0 <- Xo # simulation under policy starts from
  obs <- sim_obs(Xo, z_g, f, p, Tobs=40, nz=1, 
                 harvest = sort(rep(seq(0, .01, length=8), 5)), seed = seed_i)
  alt <- par_est(obs)
  est <- par_est_allee(obs, f, p)
  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=FALSE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f, est$p, alt$f, alt$p, x_grid, obs, seed_i)
#  posteriors_plot(gp, priors) # needs trace=TRUE!
  OPT <- optimal_policy(gp, f, est$f, alt$f,
                        p, est$p, alt$p,
                        x_grid, h_grid, sigma_g, 
                        est$sigma_g, alt$sigma_g, 
                        delta, xT, profit, reward, OptTime)
  plot_policies(x_grid, OPT$gp_D, OPT$est_D, OPT$true_D, OPT$alt_D)
  dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
  sim_plots(dt, seed=seed_i)
  profits_stats(dt)
```

```{r}
est
alt
```
